The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
Results from Table 1 and Figure 1

When looking by race, whites were the group with the lowest mean fear and Asians were the group with the highest. This finding is consistent with the hypothesis that the most privileged social group in terms of race has the lowest level of fear.

@@

>>>>

@@

When looking by race, whites were the group with the lowest mean fear and Asians were the group with the highest. This finding is aligned with the hypothesis that the most privileged social group in terms of race has the lowest level of fear. Additionally, our visualizations show the compounding effects of both race and gender----consistent with the framework of intersectionality [@mccall2005]----that the rates of reporting fear at night is higher when the group is marginalized both racially and gender-wise. For example, except for the Transgender respondents, NHPI Females, Asian Females and AIAN females reported the highest rates of fear, while White males reported the lowest rates of fear.
